Estimating Output Loss due to being Unrecognized as States

### 2019-03-07 paper/paper.tex
Format the regression table #44
Use the R script to create a one-column table. Then manually revise it. Finally, incorporate it into the paper.

>>>>

\begin{table}[ptb]
\caption{Estimated coefficients on mean light intensity and year dummies}%
\label{estimates}%
\input{income_light_cfe_yfe_result_revised.tex}\\
{\scriptsize \textit{Notes}: 
	Estimated coefficients from equation (\ref{gdp}) are reported with standard errors clustered at the country and year levels in parentheses. *** indicates statistically significant at the 1\% level; ** 5\%.
}
\end{table}
